### 2021-06-05 treatise-pdflatex/1_introduction.tex
Import bibliography for article

Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], which reduces the number of paths, and it is now that a recent development called compressive sensing may help.

>>>>

Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite {ALS14}, which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
